From Reversible Programs to \\ Univalent Universes and Back

### 2021-09-05 Pi+/paper/ufin.tex
Fix Pi-types

The semantics interprets $\PiLang$-types as objects in $\BFin$, 1-combinators as isomorphisms, and for every pair of 1-combinators
related by a 2-combinator, their interpretations in~$\BFin$ are equal.  The groupoid $\BFin$ is strict, since the
collection of isomorphisms is a set, that is, a discrete category. There is no explicit witness for the equality of two
isomorphisms, since we can decide by evaluating two bijections whether they are equal. To be able to establish
completeness for $\PiLang$, we want a witness for this equality, so that we can quote back to the syntax and produce a
2-combinator witnessing the equality of the corresponding 1-combinators.

>>>>

The semantics interprets types of $\PiLang$ as objects in $\BFin$, 1-combinators as isomorphisms, and for every pair of 1-combinators
related by a 2-combinator, their interpretations in~$\BFin$ are equal.  The groupoid $\BFin$ is strict, since the
collection of isomorphisms is a set, that is, a discrete category. There is no explicit witness for the equality of two
isomorphisms, since we can decide by evaluating two bijections whether they are equal. To be able to establish
completeness for $\PiLang$, we want a witness for this equality, so that we can quote back to the syntax and produce a
2-combinator witnessing the equality of the corresponding 1-combinators.
